%This is a LaTeX template for homework assignments
\documentclass[a4wide,14pt]{extarticle}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=18mm,
 top=18mm,
 }
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{kotex}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{tcolorbox}


\begin{document}

\setstretch{1.0}


\section*{English Test}
Name: \line(1,0){120} \, %you can change the length of the lines by changing the number in the curly brackets
\\Date: \line(1,0){120} \,

\setstretch{1.5}



\begin{enumerate}[label=$\spadesuit$]

%    \item \textbf{다음 괄호 안에서 문맥에 적절한 것을 고르시오.}
%
%    \begin{enumerate}[label={\textbf{\arabic*.}}]
%        \item     현재시제: Does she drive to work?
%        \\과거시제: \line(1,0){200} \, ?
%        \\미래표현: Will \line(1,0){200} \, ?
%        \\          = \line(1,0){200} \, ?
%    \end{enumerate}
%
%    \item \textbf{주어진 동사를 문맥에 알맞은 형태로 써넣으시오.}
%
%        \begin{enumerate}[label={\textbf{\arabic*.}}, start=2]
%            \item (finish) When you \line(1,0){120} \, studying, I'll take you to the new Chinese restaurant.
%            \item (make) She \line(1,0){120} \, spaghetti for me the other day.
%            \item (snow) If it \line(1,0){120} \, this weekend, we'll go skiing.
%            \\
%        \end{enumerate}


\item \textbf{다음 괄호 안에서 문맥에 적절한 것을 고르시오.}

	\begin{enumerate}[label={\textbf{\arabic*.}}]
		 \setstretch{1.5} % Add every time in the front 'cause it beautiful
		 \item They understand that bad (nutrition / courtesy) is the cause of most chronic diseases.

		 \item I figured it was okay for her to (sip / chop) my wine even if it was not good manners.

		 \item At the party, John asked Mary whether she wanted to take some (circumstances / refreshments).

		 \item Is co-teaching a (seasoning / fad) or the future for teaching students with disabilities?

		 \item Choosing a(n) (occupation / beverage) is one of the most important decisions you make in your
		 life.

		 \item Harsh working conditions were (cosmetic / prevalent) during the Industrial Revolution.

		 \item What your (outfit / ingredient) looks like is important in choosing the right accessories.51

		 \item Scientists think that our brains (shrink / alter) two percent per decade.

		 \item (Routine / Masculine) examination of the teeth is recommended at least every year.

		 \item The magazine featured home-style Southern (cuisine / engagement) such as fried chicken.


   \end{enumerate}

\newpage

\item \textbf{다음 괄호 안에서 문맥에 적절한 것을 고르시오.}

	\begin{enumerate}[label={\textbf{\arabic*.}}]

	\item Michelle has launched a campaign against childhood (obesity / diagnosis).

	\item The sickness came on suddenly, beginning with (fever / hygiene), chills and stomach cramps.

	\item Some might think that losing a(n) (limb / ailment) or suffering a major spinal cord injury is the
	end of the world.

	\item The policies ensure access to a clean drinking water supply and (lethal / sanitary) facilities.

	\item I think it's important if someone's going to (sneeze / doze), they should cover their mouth.

	\item He maintained boxing (workóuts / injections) throughout the rest of his life at Gleason's Gym.

	\item The camp is put under (perspiration / quarantine) to keep the virus from spreading.

	\item Children who suffered abuse must receive proper protection and an effective (remedy /
	infection).

	\item The (epidemic / checkup) lasted for two years and killed an estimated one third of the population.

	\item Researchers who have observed the homeless say tent dwellers often have a drug or alcohol (diabetes / addiction).

	\end{enumerate}

\newpage

\item \textbf{다음 빈칸에 들어갈 적절한 말을 아래에서 찾아 쓰시오.}

	\begin{tcolorbox}
		\begin{center}
		workout, alter, sneeze, obesity, remedy, doze, outfit
		\end {center}
	\end{tcolorbox}

		\begin{enumerate}[label={\textbf{\arabic*.}}, start=1]
			\item Color has the ability to completely \line(1,0){80}\ the atmosphere of your home.

			\item If you experience any side effects from a natural \line(1,0){80}, stop using it immediately.

			\item You have to wear a brand-new \line(1,0){80}\ that matches or complements your hair style.
		\end{enumerate}


\item 다음 괄호 안에서 문맥에 적절한 것을 고르시오.


	 \begin{enumerate}[label={\textbf{\arabic*.}}, start=1]

	 	\item This is a point where you could easily (inject / deject) your thoughts into the discussion.

	 	\item Ongoing bad breath may be a (symptom / syndrome) of tooth decay or digestive health
	 	issues.

	 	\item Tom, wearing a white summer shirt soaked in (respiration / perspiration), was excited
	 	about the game.

	\end{enumerate}


\item 다음 주어진 단어를 빈칸에 적절한 형태로 바꿔 쓰시오.

	\begin{enumerate}[label={\textbf{\arabic*.}}, start=1]

		\item Society began to realize individuals were consuming highly \line(1,0){80}\ substances. (addict)

		\item By clearing away the waste, these programs have made working conditions more \line(1,0){80}\. (sanitation)

		\item It's no wonder that an old woman has trouble maintaining a \line(1,0){80}\ diet. (nutrition)



	\end{enumerate}

\newpage

\item 다음 중 밑줄 친 말과 유사한 의미를 가진 단어를 고르시오.

	\begin{enumerate}[label={\textbf{\arabic*.}}, start=1]

		\item The band continued to perform, but their crowds were beginning to \underline{shrink} dramatically.

		\begin{enumerate}[label={(\alph*)}]
			\item refuse
			\item desert
			\item scream
			\item diminish
			\item escalade
		\end{enumerate}

		\item As water is an essential \underline{ingredient} for any beer, good quality water is needed in order to create the best beer.

		\begin{enumerate}[label={(\alph*)}]
			\item reason
			\item element
			\item disaster
			\item assignment
			\item allowance
		\end{enumerate}

		\item Drink water before, during, and after your \underline{workout}, warm up gradually, and exercise in a cool environment.

		\begin{enumerate}[label={(\alph*)}]
			\item dartcraft
			\item solution
			\item exercise
			\item checkup
			\item trial
		\end{enumerate}

	\end{enumerate}

\newpage

\item 다음 글의 밑줄 친 부분 중, 문맥상 낱말의 쓰임이 적절하지 \underline{않은} 것은?

\begin{tcolorbox}
	Of all athletic wear, football uniforms and equipment present the most significant
	\textcircled{1} \underline{barrier} to heat dissipation. Even with loose-fitting porous jerseys, the wrappings padding, helmet, and other objects of ''armor`` effectively seal off 50\% of the body's surface from the benefits of \textcircled{2} \underline{evaporative}	cooling. Just wearing the 6 to 7 kg of football equipment significantly adds to the metabolic load, without considering the \textcircled{3}	\underline{thermal} challenge from a hot artificial playing suřface. The large body size of these athletes further \textcircled{4} \underline{reduces} the heat load, particularly for offensive and defensive	linemen. They \textcircled{5} \underline{possess} a relatively small surface area-to-mass ratio and a higher	percentage of body fat than players at other positions.


\end{tcolorbox}


\newpage

\item (A), (B), (C)의 각 네모 안에서 문맥에 맞는 낱말로 가장 적절한 것은?

\begin{tcolorbox}

	An alternative possibility for satisfying self-expressive needs and meaning in work
	can occur through leisure and avocational activities. Avocational activities are
	(A) (avoided / persued) systematically and consecutively for their own sake; the
	objective is something other than (B) (monetary / unfavorable) gain, which may
	incidentally occur. Leisure and avocational activities can be especially rewarding
	when other parts of one's life are not going as smoothly as one would like. People
	who put all their eggs in one basket, so to speak, (whether work, an intimate
	relationship, or parenthood) risk an imbalance that can (C) (adversely/ beneficially)affect their well-being as well as that of people around them. Leisure is hardly goofing off. Leisure provides a respite from work responsibilities and pressures.

\end{tcolorbox}

	\begin{enumerate}[label={(\arabic*)}, start=1]
		\item persued $\cdots$ monetary $\cdots$ beneficially
		\item avoided $\cdots$ monetary $\cdots$ beneficially
		\item persued $\cdots$ menotary $\cdots$ adversely
		\item avoided $\cdots$ unfavorable $\cdots$ adversely
		\item persued $\cdots$ unfavorable $\cdots$ adversely
	\end{enumerate}

\end{enumerate}


%
%\begin{enumerate}[label=$\spadesuit$]
%    \item \textbf{다음 중 어법에 맞는 것을 고르시오.}
%        \begin{enumerate}[label={\textbf{\arabic*.}}, start=8]
%            \item We saw Tim yesterday. He [ is reading / was reading] a book in a cafe.
%            \item A: When will Peter leave for Japan?
%            \\B: He [was leaving / is leaving] tomorrow morning.
%        \end{enumerate}
%\end{enumerate}
%
%
%
%\begin{enumerate}[label=$\spadesuit$]
%    \item \textbf{10. 다음 빈칸에 들어갈 말이 바르게 짝지어진 것을 고르시오.}
%    \begin{tcolorbox}
%        \begin{enumerate}
%        \setstretch{1.0}
%            \item I \line(1,0){60} \, need your MP3 player right now.
%            \item She \line(1,0){60} \,digging a hole in the garden the other day.
%            \item The chef \line(1,0){60}\, testing a new dish. Don't distrub him.
%        \end{enumerate}
%    \end{tcolorbox}
%
%    \begin{enumerate}\setstretch{1.0}
%        \item don't $\cdots$ is $\cdots$ was
%        \item don't $\cdots$ was $\cdots$ is
%        \item didn't $\cdots$ is $\cdots$ was
%        \item didn't $\cdots$ was $\cdots$ is
%        \item don't $\cdots$ is $\cdots$ is
%    \end{enumerate}
%
%\end{enumerate}
%\setstretch{1.5}
%
%
%
%\begin{enumerate}[label=$\spadesuit$]
%    \item \textbf{빈칸에 주어진 동사의 현재완료형을 쓰시오.}
%    \begin{enumerate}[label={\textbf{\arabic*.}}, start=11]
%        \item  (work) Mr.Lee \line(1,0){80}, \line(1,0){80} at the bank for five years.
%        \item (know) Judy \line(1,0){80} \, \line(1,0){80} \, her boyfriend for a year.
%        \item (lose) I can't see anything. I \line(1,0){80} \, \line(1,0){80} \, my glasses.
%    \end{enumerate}
%\end{enumerate}
%
%
%\begin{enumerate}[label=$\spadesuit$]
%    \item \textbf{주어진 두 문장을 괄호 안의 단어를 이용하여 한 문장으로 완성하시오.}
%    \begin{enumerate}[label={\textbf{\arabic*.}}, start=14]
%        \item She started using this computer three years ago. She still uses it. (use)
%        \\ $\rightarrow{}$She \line(1,0){80} \,  \line(1,0){80} \, this computer for three years.
%        \item I lost my wallet. I have no money now. (lose)
%        \\ $\rightarrow{}$I \line(1,0){80} \, \line(1,0){80} \, my wallet.
%    \end{enumerate}
%    \item \textbf{주어진 문장과 같은 뜻이 되도록 알맞은 표현을 고르시오.}
%    \begin{enumerate}[label={\textbf{\arabic*.}}, start=16]
%        \item I have a car. I bought it four months ago.
%        \\ = I have the car [for / since] four months.
%        \item I live in Gwang-ju. I moved here in 2006.
%        \\ = I have lived in Gwang-ju [for / since] 2006.
%    \end{enumerate}
%
%\end{enumerate}
%
%
%
%\begin{enumerate}[label=$\spadesuit$]
%    \item \textbf{18. 다음 동사 중 동사의 변화형이 바른 것을 고르시오.}
%    \setstretch{1.0}
%    \begin{enumerate}
%        \item break $\cdots$ broke $\cdots$ breaken
%        \item blow $\cdots$ blew $\cdots$ blown
%        \item buy $\cdots$ buyed $\cdots$ buyed
%        \item take $\cdots$ took $\cdots$ took
%        \item fall $\cdots$ fell $\cdots$ fell
%    \end{enumerate}
%    \setstretch{1.5}
%
%
%
%    \item \textbf{19. 다음 중 동사의 변화형이 바르지 \underline{않은} 것을 고르시오.}
%    \setstretch{1.0}
%        \begin{enumerate}
%            \item go $\cdots$ went $\cdots$ gone
%            \item grow $\cdots$ grew $\cdots$ grown
%            \item hit $\cdots$ hit $\cdots$ hit
%            \item think $\cdots$ thought $\cdots$ thought
%            \item hide $\cdots$ hid $\cdots$ hid
%        \end{enumerate}
%        \setstretch{1.5}
%
%\newpage
%
%    \item \textbf{20. 다음 중 괄호 안의 말을 알맞게 고친 것끼리 바르게 짝지은 것은?}
%        \begin{tcolorbox}
%        He (start) to make a model airplane last week and (just, finish) it.
%        \end{tcolorbox}
%        \setstretch{1.0}
%        \begin{enumerate}
%            \item starts $\cdots$ just finished
%            \item has started $\cdots$ has just finished
%            \item has started $\cdots$ just finished
%            \item started $\cdots$ just finishes
%            \item started $\cdots$ has just finished
%        \end{enumerate}
%        \setstretch{1.5}
%
%\end{enumerate}
%

\end{document}